Papers

### 2025-09-12 papers.qmd
update

- Butters, A., Marshall, M. B., Pinfield, S., Stafford, T., Bondarenko, A., Neubauer, B., Nuske, R., Schwidlinski, P., & Denecke, H. (2025). [Applicants as Reviewers: Evaluating the Risks, Benefits, and Potential of Distributed Peer Review for Grant Funding Allocations](https://doi.org/10.6084/m9.figshare.29994841.v2) (RoRI Working Paper No. 17). https://doi.org/10.6084/m9.figshare.29994841.v2

>>>>

- Butters, A., Marshall, M. B., Pinfield, S., Stafford, T., Bondarenko, A., Neubauer, B., Nuske, R., Schwidlinski, P., & Denecke, H. (2025). [Applicants as Reviewers: Evaluating the Risks, Benefits, and Potential of Distributed Peer Review for Grant Funding Allocations](https://doi.org/10.6084/m9.figshare.29994841) (RoRI Working Paper No. 17). https://doi.org/10.6084/m9.figshare.29994841
